---
title: "AIDS DRUGS"
author: Rita Bowden
date: 05/04/2019
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
avast <-read.csv(file="avastivironal.csv",header=TRUE)
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

This data is from 2019 Final from AVCDK github

Research Question:

$H_0:$ The preventive drug avacavirinol has no effect whether one contracts AIDS or not

$H_A:$ The preventive drug avacavirinol has an effect whether one contracts AIDS or not 


A new  preventative aides (abacavirinol) is under test in clinical trials. Analyze the effectiveness of this drug across the board. Consider population subgroups by gender, drug use, and sexual orientation. 
I Would like to know if treatment works in the population. And how  effective the  drugs is among IV drug users, in the LBGT community and if gender has any role on the effectiveness of the vaccine.  

# Methods


<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

We use a barchart for the graphical description, 
Chi -squared test to test the hypothesis that the AIDS drug avacavirinol  is effective in treating people that contracted AIDS

#Results 

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->
 We use a barchart to show the AIDS treatment using the placebo versus the drug

```{r}
barchartGC(~infected+treatment,type='percent', data=avast)
```

The barchart shows a significant difference between the population that took the preventative AIDS drug and those that took the placebo, more of the population that took the placebo contracted AIDS


### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

Numerical summary is a cross tabulation
```{r}
xtabs(~infected+treatment, data=avast)
```

This table shows a lower incidence of contracting AIDS when they took the drug than when they took the placebo

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
chisqtestGC (xtabs(~infected+treatment, data=avast))
```

The P value is 0 so we reject the null hypothesis. The hypothesis is that the AIDS drug avacavirinol is effective in preventing AIDS in the general population based on the results of the chi-squared test of independence 

# Discussion and Conclusion
The hypothesis is that the AIDS drug is effective in preventing AIDS based on the result of the chi-squared test of independence,.
   We reject the null hypothesis since P is 0, we  have enough evidence to reject the null hypothesis and accept the alternative hypothesis that the AIDS drug is effective in preventing AIDS. If a person took the drug it is less likely to be infected by AIDS than if the person took the placebo
   
   
# Introduction 
$H_0:$1: there is no relationship between effectiveness of the drug and sex


#Methods


#Results


# Graphical Descriptive Results

```{r}
barchartGC(~sex+treatment,type='percent', data=avast)
```
#Numerical Descriptive Results


```{r}
xtabs(~sex+treatment, data=avast)
```

Inferential Results
```{r}
chisqtestGC (xtabs(~sex+treatment, data=avast))
```


# Discussion and Conclusion

#Introduction

#Methods
```{r}

```

#Results

#Descriptive Results

#Graphical Descriptive Results


```{r}
barchartGC(~LBGT+treatment,type='percent', data=avast)
```

#Numerical DEscriptive Results
```{r}
xtabs(~LBGT+treatment, data=avast)
```
#Inferential REsults
```{r}
chisqtestGC (xtabs(~LBGT+treatment, data=avast))
```


## Discussion and Conclusion





#Introduction




#Methods


#Results


# Descriptive Results



#Graphical Descriptive Results
```{r}
barchartGC(~Ivdrug+treatment,type='percent', data=avast)
```



#Numerical DEscriptive Results
```{r}
xtabs(~Ivdrug+treatment, data=avast)
```
#Inferential REsults

```{r}
chisqtestGC (xtabs(~Ivdrug+treatment, data=avast))
```

## Discussion and Conclusion

   



