---
title: "AIDS DRUGS"
author: Rita Bowden
date: 05/04/2019
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
avast <-read.csv(file="avastivironal.csv",header=TRUE)
avastF = filter(avast, sex=='F')
avastLBGT = filter(avast, LBGT=='yes')
avastIV = filter(avast, Ivdrug == 'user' )
```

# Introduction General Population

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?
.  
If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

# Question 1
 Did the vaccine make a difference in the general population?
 
Null Hypothesis:


A new  preventative aides (avastivirinol) is under test in clinical trials. Analyze the effectiveness of this drug across the board. Consider population subgroups by gender, drug use, and sexual orientation. 



<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

This data is from 2019 Final from AVCDK github

Research Question:

$H_0:$ The preventive drug avacavirinol has no effect whether one contracts AIDS or not

$H_A:$ The preventive drug avacavirinol has an effect whether one contracts AIDS or not 


A new  preventative aides (abacavirinol) is under test in clinical trials. Analyze the effectiveness of this drug across the board. Consider population subgroups by gender, drug use, and sexual orientation. 
I Would like to know if treatment works in the population. And how  effective the  drugs is among IV drug users, in the LBGT community and if gender has any role on the effectiveness of the vaccine.  

# Methods


<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

We use a barchart for the graphical description, 
Chi -squared test to test the hypothesis that the AIDS drug avacavirinol  is effective in treating people that contracted AIDS

#Results 
The vaccine was very much working and have a great effictiveness in the general poplutation?

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->
 We use a barchart to show the AIDS treatment using the placebo versus the drug

```{r}
barchartGC(~infected+treatment, data=avast,type='percent')
```

The barchart shows a significant difference between the population that took the preventative AIDS drug and those that took the placebo, more of the population that took the placebo contracted AIDS


### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

Numerical summary is a cross tabulation
```{r}
xtabs(~infected+treatment, data=avast)
```

This table shows a lower incidence of contracting AIDS when they took the drug than when they took the placebo

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
chisqtestGC(~infected+treatment, data=avast)
```

The P value is 0 so we reject the null hypothesis. The hypothesis is that the AIDS drug avacavirinol is effective in preventing AIDS in the general population based on the results of the chi-squared test of independence 



#Results For Female Sub Population: 
This vaccine seems to  have  a bad effect on female population, Its seem to increase odds of  the female getting AIDS VIRUS 1.5to 1bad drug. 

##Descriptive results
Here is the bar plot, numerical summary, and chi-squared test results

###Graphical Descriptive Results 
There is strong evidence that female gender has less effectiveness and should not take the treatment, compared to the placebo.



```{r}
barchartGC(~infected+treatment, data=avastF, type='percent')
```

The bar chart shows effectivness is related to gender, women are more susceptible.

Numerical Descriptive Results

The table shows a signficent difference in gender that took the drug verses those that took the placebo.

```{r}
Famtable=xtabs(~infected+treatment,data=avastF)
rowPerc( Famtable)
```



#Inferential Results
H0:H0: a substancial difference is shown between those female that took the treatment verses the one that took the placebo in the clinical studies.
```{r}
chisqtestGC(~infected+treatment, data=avastF)
fisher.test( Famtable)
```

The Pvalue is .0004 we reject the null hypothesis since the p< 0.05, the hypothesis that the effectiveness of the drug and sex are related base on the results of the chi-squared test of independence

#Results IVdrug User:
Does the IV drug make a difference in vaccine effectiveness?

#Descriptive Results
The null hypothesis is:
$H_0$: there is no relationship between the effectiveness of the drug and IVdrug
$H:A$: there is a relationship between the effictiveness of the drug and IVdrug

#Graphical Descriptive Results

There is strong evidence that treatment does have an effective on IVdrug usage 


```{r}
barchartGC(~infected +treatment,data=avastIV, type='percent')
```

This bar chart shows evidence of a difference between IVdrug use and treatment 

#Numerical Results

Numerical summary is a cross tabulation 
```{r}
xtabs(~infected+treatment, data=avastIV)
```
The table shows a difference between IVdrugs and the treatments

#Inferential Results

```{r}
chisqtestGC (~infected+treatment, data=avastIV)
```

Pvalue is 0, so we reject the null hypothesis since the P<0.05, the hypothesis is that the effectiveness of the drug and the IVdrugs are related based on the results of the chi-squared test of independence

# Results LBGT: 
sexual orientation have any effect on vaccines effectiveness 

The null hypothesis is:
$H_0$: there is no relationship between the effectiveness of the drug and sex
$H:A$: there is a relationship between the effictiveness of the drug and sex

## Descriptive Results


###Graphical Descriptive Results

we use the bar chart to show the trends between the AIDS and drug effectiveness and being LBGT
```{r}
barchartGC(~infected+treatment, data=avastLBGT, type='percent')
```
The bar chart showsthat the vaccine did have some effect.The incdent of aids is smaller,than the ones who didn't.


#Numerical Descriptive Results
Numerical summary is a cross tabulation 

```{r}
xtabs(~infected+treatment, data=avastLBGT)
```

#Inferential Results

```{r}
chisqtestGC (xtabs(~infected+treatment, data=avastLBGT))
```


Pvalue is 0, so we reject the null hypothesis since the P<0.05, the hypothesis is that the effectiveness of the drug and being LBGT are related based on the results of the chi-squared test of independence

## Discussion and Concludion

LBGT The results demonstrate that the vaccine is very effective in the LBGT population. The null hypothesis was that sexual orientation does not effect the effectiveness of the vaccine.

The vaccine looks like it is effective in the general population. It seems to be unaffected by gender or Sexual orientation. The testing indicates we reject the null hypotheses and accept that the vaccine appears to have somewhat of a  positive effect, which is slightly less for some subgroups including IV drug users.



